### 2015-09-04 qdpm_paper.tex
tried to fix permisions

    \begin{table}[htpb]
        \centering
        \caption{$\Delta \tau = 150$}
        \label{tab:label}
        \begin{tabular}{c c c}
            \hline\hline
         L            & 8x8 Gap  & 16x16  \\ 
            \hline
         frac 1.0     &          & \\
            \hline
         Dimer origin &  0.03230 & 0.00806 \\
         $Z_2$ origin &  0.00787 & 0.00198  \\
         $Z_3$ origin &  NA      & NA \\
            \hline
         frac 0.9     &          & \\
            \hline
         Dimer origin &  0.00419 & 0.00429 \\
         $Z_2$ origin &  0.00216 & 0.00129  \\
         $Z_3$ origin &  0.00346 & 0.00359 \\
            \hline
         frac 0.5     &          & \\
            \hline
         Dimer origin &          & 0.02049 \\
         $Z_2$ origin &          & 0.00614  \\
         $Z_3$ origin &          & 0.01927  
        \end{tabular}
    \end{table}

>>>>

    \begin{table}[htpb]
        \centering
        \caption{$\Delta \tau = 150$}
        \label{tab:label}
        \begin{tabular}{c c c c}
            \hline\hline
         L            & 8x8 Gap                               & 12x12                            & 16x16                               & 18x18 \\ 
            \hline                                                                                                                           
         frac 1.0     &                                       &                                  &                                     &  \\
            \hline                                                                                                                           
         Dimer        &  $ 0.03230 \pm 0.01142$               & $ 0.01430 \pm 0.00034 $          & $0.00806 \pm 0.00023$               & \\
         $Z_2$ origin &  $ 0.00787 \pm 5.3\times 10^{-6} $    & $ 0.00344 \pm 9.0\times 10^{-7}$ & $0.00198 \pm 3.8\times 10^{-6} $    &  \\
         $Z_3$ origin &  NA                                   & NA                               & NA                                  & \\
            \hline                                                                                                                         
         frac 0.9     &                                       &                                  &                                     &  \\
            \hline                                                                                                                          
         Dimer origin &  $ 0.00419 \pm 8.1\times 10^{-6} $    & $ 0.00406 \pm 1.7\times 10^{-5} $ & $0.00429 \pm 6.6\times 10^{-6} $   &  $ 0.00405 \pm 1.6\times 10^{-5} $\\
         $Z_2$ origin &  $ 0.00216 \pm 1.5\times 10^{-6} $    & $ 0.00141 \pm 8.4\times 10^{-7} $ & $0.00129 \pm 1.8\times 10^{-6} $   &  $ 0.00126 \pm 1.7\times 10^{-6} $\\
         $Z_3$ origin &  $ 0.00346 \pm 3.8\times 10^{-6} $    & $ 0.00348 \pm 5.1\times 10^{-6} $ & $0.00359 \pm 3.5\times 10^{-6} $   &  $ 0.00355 \pm 3.3\times 10^{-6}$\\
            \hline                                                                                                                          
         frac 0.5     &                                       &                                   &                                    & \\
            \hline                                                                                                                          
         Dimer origin &                                       & $ 0.02075 \pm 8.9\times 10^{-5} $ & $0.02049 \pm 0.00011 $             &  $ $ \\
         $Z_2$ origin &                                       & $ 0.00615 \pm 2.2\times 10^{-6} $ & $0.00614 \pm 2.8\times 10^{-6} $   &  $ $ \\
         $Z_3$ origin &                                       & $ 0.01939 \pm 2.2\times 10^{-5} $ & $0.01927 \pm 0.00002 $             &  $ $  
        \end{tabular}
    \end{table}
